### 2022-03-23 src/text/2-package-subsections/stats.tex
Added ref

\subsection{gammapy.stats}
\label{ssec:gammapy-stats}
\todo{Regis Terrier}
Statistics methods

>>>>

\subsection{gammapy.stats}
\label{ssec:gammapy-stats}
\todo{Regis Terrier}

The gammapy.stats subpackage contains the fit statistics and associated statistical estimators
that are commonly used in gamma-ray astronomy.
In general, gamma-ray observations count Poisson-distributed events at various sky positions,
and contain both signal and background events. Estimation of the number of signal events is done
through likelihood maximization. In Gammapy, the fit statistics are Poisson log-likelihood functions
normalized like chi-squares, i.e. they follow the expression $2 \times log L$, where $L$ is the
likelihood function used.

The statistic function used when the expected number of background events is known
is \emph{Cash}. It used When the number of background events is unknown, one has to
use a background estimate :math:`n_{bkg}` taken from an off measurement where only background events
are expected. In this case, the statistic function is ``WStat`` (see :ref:`wstat`).
